---
title: "R Markdown and Leaflet Data Products Week 2 Assignment"
author: "Ella"
date: "July 4, 2017"
output: html_document
---

## Overview

This R Markdown document, features a map created with Leaflet, will display Disney Parks around the world. 

## Background
Disney parks are located at 6 locations around the world:
1. California, USA
2. Flordia, USA
3. Paris, France
4. Tokyo, Japan
5. Shanghai, China
6. Hongkong

## Preparation
Load leaflet library
```{r preparation}
library(leaflet)
```

## Create the map
```{r}
disneysIcon <- makeIcon("disneyIcon.JPG",
  iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

disneysLatLong <- data.frame(
  lat = c(33.812511, 28.385071, 48.8722, 35.6329, 31.1453, 22.3130),
  lng = c(-117.918976, -81.563808, 2.7758, 139.8804, 121.6573, 114.0413))

disneysSites <- c(
  "<a href='https://disneyland.disney.go.com/destinations/'>Disney California</a>",
  "<a href='https://disneyworld.disney.go.com/'>Disneyworld Flordia</a>",
  "<a href='http://www.disneylandparis.com/en-us/'>Disney Paris</a>",
  "<a href='http://www.tokyodisneyresort.jp/en/'>Disney Tokyo</a>",
  "<a href='https://www.shanghaidisneyresort.com/en/'>Disney Shanghai</a>",
  "<a href='https://www.hongkongdisneyland.com/?located=true'>Disney Hong Kong</a>"
)

disneysLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = disneysIcon, popup = disneysSites)
```

For more info, click the Disney Parks on the map to connect to its website.
